### 2017-11-10 manuscript.rmd
replaced all mclapply with doParallel foreach

	# The rest can be installed from CRAN
	library( ape )
	library( digest )
	library( geiger )
	library( ggrepel )
	library( gridExtra )
	library( magrittr )
	library( parallel )
	library( phytools )
	library( stringr )
	library( tidyverse )

>>>>

	# The rest can be installed from CRAN
	library( ape )
	library( digest )
	library( geiger )
	library( ggrepel )
	library( gridExtra )
	library( magrittr )
	library( phytools )
	library( stringr )
	library( tidyverse )
